A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-20 manuscript.Rmd
fixed typo

Figure \@ref(fig:schematic) gives an overview of how the four components of our workflow interact to ensure computational reproducibility. Before we describe the four components in more detail, we begin with a minimal description of the roles of each component. In the remainder of this tutorial, we will further detail each of the four components of our workflow. The first component is version control. Version control manages changes to files (e.g., data and code) over time so that you can recall specific versions of files later or revert the entire project to a past state. Version control offers snapshots of your workflow at different time points identified by a unique identifier. The different frames in the z-axis of Figure  \@ref(fig:schematic) illustrate the different versions of the project. How different parts of a analysis and a report of it relate and in what order they need to be executed is documented using dependency management. The arrows visualize dependencies, such as an analysis depending on the availability of a particular data file. Third, all computer code (such as a statistical analyses in R) is executed in a virtual environment that guarantuees exact reproduction of results independent of the host operating system, the locally installed R version, and installed package versions. Finally, dynamic document generation (also known as the literate programming paradigm) interweaves human-readable code and computed results (such as point estimates, p values, or confidence intervals) to eliminate inconsistency errors such as those arising from copy\&paste errors.

@@

Each tool in the workflow reduces the chances of non-reproducibility. Dynamic reporting with R Markdown guarantees consistency between computational results and their reporting; Version control with Git ensures permanence and consistency across multiple versions of data and code; Dependency management with Make provides defined entry-points while mapping out dependencies between all components of a project; containerization with Docker guarantuees full computational reproducibility. We believe that the proposed combination of tools does not restrict researchers but enables them to operate on a solid basis to deliver transparent and sustainable research.

@@

The proposed workflow leverages various existing tools that are partly integrated into RStudio already. Parts of the proposed workflow have been integrated into stand-alone packages [such as `worcs`, @worcs; `workflowr`, @workflowr; or `holepunch` @holepunch], which we recommend to beginners; in particular, `worcs` is a step-by-step procedure with best practices for Open Science from preregistration to publication. Still those approaches do either not guarantuee full computational reproducibility or rely on proprietary service providers. We hope that with increasing awareness of the challenges of computational reproducibility, the increased demand for unified and open solutions will lead to better integration of existing tools and services to allow reproducible workflows to become a standard in psychological research.

>>>>

Figure \@ref(fig:schematic) gives an overview of how the four components of our workflow interact to ensure computational reproducibility. Before we describe the four components in more detail, we begin with a minimal description of the roles of each component. In the remainder of this tutorial, we will further detail each of the four components of our workflow. The first component is version control. Version control manages changes to files (e.g., data and code) over time so that you can recall specific versions of files later or revert the entire project to a past state. Version control offers snapshots of your workflow at different time points identified by a unique identifier. The different frames in the z-axis of Figure  \@ref(fig:schematic) illustrate the different versions of the project. How different parts of a analysis and a report of it relate and in what order they need to be executed is documented using dependency management. The arrows visualize dependencies, such as an analysis depending on the availability of a particular data file. Third, all computer code (such as a statistical analyses in R) is executed in a virtual environment that guarantees exact reproduction of results independent of the host operating system, the locally installed R version, and installed package versions. Finally, dynamic document generation (also known as the literate programming paradigm) interweaves human-readable code and computed results (such as point estimates, p values, or confidence intervals) to eliminate inconsistency errors such as those arising from copy\&paste errors.

@@

Each tool in the workflow reduces the chances of non-reproducibility. Dynamic reporting with R Markdown guarantees consistency between computational results and their reporting; Version control with Git ensures permanence and consistency across multiple versions of data and code; Dependency management with Make provides defined entry-points while mapping out dependencies between all components of a project; containerization with Docker guarantees full computational reproducibility. We believe that the proposed combination of tools does not restrict researchers but enables them to operate on a solid basis to deliver transparent and sustainable research.

@@

The proposed workflow leverages various existing tools that are partly integrated into RStudio already. Parts of the proposed workflow have been integrated into stand-alone packages [such as `worcs`, @worcs; `workflowr`, @workflowr; or `holepunch` @holepunch], which we recommend to beginners; in particular, `worcs` is a step-by-step procedure with best practices for Open Science from preregistration to publication. Still those approaches do either not guarantee full computational reproducibility or rely on proprietary service providers. We hope that with increasing awareness of the challenges of computational reproducibility, the increased demand for unified and open solutions will lead to better integration of existing tools and services to allow reproducible workflows to become a standard in psychological research.
